### 2024-07-12 cognitive-bias.qmd
20240712 - plot title and axis titles

```{r}
#| fig-cap: "Histogram of number of coins that flip heads-up in a simulation of 10 coin flips (with 100,000 replications)."
#| label: fig-simulationOf10CoinFlips
#| code-fold: true

@@

ggplot(
  data = simulationOfFlipping10Coins,
  mapping = aes(
    x = numHeads,
    fill = highlight)
) +
  geom_histogram(
    color = "#000000",
    bins = 11
  ) +
  scale_x_continuous(
    breaks = 0:10
  ) +
  scale_fill_manual(
    values = c(
      "yes" = "tomato",
      "no" = "gray")
  ) +
  theme_classic() +
  theme(legend.position = "none")
```

>>>>

```{r}
#| fig-cap: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| label: fig-simulationOf10CoinFlips
#| code-fold: true

@@

ggplot2::ggplot(
  data = simulationOfFlipping10Coins,
  mapping = aes(
    x = numHeads,
    fill = highlight)
) +
  geom_histogram(
    color = "#000000",
    bins = 11
  ) +
  scale_x_continuous(
    breaks = 0:10
  ) +
  scale_fill_manual(
    values = c(
      "yes" = "tomato",
      "no" = "gray")
  ) +
  labs(
    x = "Number of Coins Flipped Heads (out of 10 Coin Flips)",
    y = "Frequency",
    title = "Histogram of Number of Coins that Flip Heads-Up\nin a Simulation of 10 Coin Flips\n(with 100,000 Replications)."
  ) +
  theme_classic() +
  theme(legend.position = "none")
```
